Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal Model to Beyond

### 2024-04-24 main.tex
:pencil: Update background

\begin{abstract}
	This paper investigates the limit to which a passive \gls{ris} can redistribute the singular values of a point-to-point \gls{mimo} channel.
	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
	% An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., degree of freedom and condition number).
	To quantify the shaping capability of diagonal and \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
	Those results help to explain the shaping advantage from off-diagonal entries in terms of subchannel rearrangement and subspace alignment.
	% Subchannel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward subchannels.
	% Subspace alignment generalizes phase matching in \gls{siso} and introduces a trade-off between multiplicative backward-forward and additive direct-indirect channel combinations.
	% Those channel shaping designs have two major implications.
	% First, they demystify the performance gain from off-diagonal entries in terms of {subchannel rearrangement} and {subspace alignment}.
	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
	% Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
	As a side product, we tackle \gls{ris}-aided \gls{mimo} rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-based approach.
	Simulation results highlight that \gls{bd}-\gls{ris} provides a wider dynamic range and better trade-off on channel singular values, while its power and rate gains over diagonal \gls{ris} scale with \gls{mimo} dimensions.

@@

\begin{section}{Introduction}
	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
	This is empowered by the recent advances in \gls{ris}, a programmable metasurface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
	The most popular \gls{ris} application is \emph{joint beamforming} design with transceivers, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
	Since coherent scattering can be decomposed as equal-gain combining and transmission, \gls{ris} elements usually offer a squared asymptotic performance (e.g., second-order array gain and fourth-order power scaling law \cite{Zhao2022}) than transceiver antennas.
	% However, a large-dimensional \gls{ris} is generally required to compensate the power loss from double fading.
	On the other hand, \gls{ris} can also be employed for \emph{backscatter modulation} by periodically switching its reflection pattern.
	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) that can be either integrated into the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or exploited by surrounding low-power devices for energy-efficient uplink communications \cite{Liang2020,Zhao2022a,Yang2024}.

	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
	The answer depends heavily on the scattering model and hardware architecture.
	Most existing works assumed that each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
	This ideally translates to a diagonal scattering matrix with unit-magnitude entries, which only controls the phase of the scattered waves but cannot redistribute their amplitude.
	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} which physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices respectively.}
	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate losslessly within the circuit and depart partially from any element in the same group.
	It can thus control both the amplitude and phase of the scattered wave without power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
	Such a powerful model can be realized at reduced hardware complexity using tree- and forest-connected architectures using graph theory \cite{Nerini2024}.
	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
	Its superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
	When it comes to \gls{mimo}, most existing works are limited to very specific scenarios.
	For example, the authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design under the assumption of unitary \gls{ris} without direct link.
	Received power maximization problem is extended to \gls{mimo} for continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} scattering matrices, but they only considered single-stream transmission with given precoder and combiner (which is equivalent to \gls{siso}).
	Transmitter-side \gls{bd}-\gls{ris} design over statistical \gls{csi} has been introduced to massive \gls{mimo} networks for improved spectral efficiency \cite{Mishra2024}, but was again constrained to unitary \gls{ris} without direct link.
	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
	Although the results are insightful, it remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with \gls{mimo} dimensions.
	% Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.

	Channel shaping is different from passive beamforming since the \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the channel itself, instead of optimizing for a specific performance metric.
	This not only allows one to decouple the joint \gls{ris}-transceiver design, but also unveils the fundamental limits of wave manipulation and provides an all-in-one tool for various wireless applications.
	Relevant designs can be classified into two categories:
	\begin{itemize}
		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are sensitive to minor perturbations but precisely related to the capacity and diversity-multiplexing trade-off. It has been mainly studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
		\item \emph{Power centric:} Focus on the second-order characteristics of the equivalent channel matrix, which are useful in \gls{siso} and \gls{miso} but less informative in \gls{mimo}. It has been mainly studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
	\end{itemize}

	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general scenario with direct link and arbitrary group size.
	On the other hand, \gls{bd}-\gls{ris} has been mainly investigated for beamforming and its channel shaping potential in \gls{mimo} has not been fully understood.
	% the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
	The contributions are summarized below.

@@

\begin{section}{Power Gain and Achievable Rate Maximization}\label{sc:power_rate}
	\begin{subsection}{Channel Power Gain}\label{sc:power}
		The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct-less \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
		Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
		\begin{mini!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
			\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_block_unitary}}{}
		\end{mini!}
		which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary but still has no trivial solution.
		One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
		\begin{mini!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
			\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
		\end{mini!}
		which have global optimal solutions
		\begin{equation}
			\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
			\label{eq:orthogonal_procrustes_solution}
		\end{equation}
		where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid unitary \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.

>>>>

\begin{abstract}
	This paper investigates how significantly a passive \gls{ris} can redistribute the singular values of a \gls{mimo} point-to-point channel.
	% the limit to which
	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements.
	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to subchannel rearrangement and subspace alignment.
	This powerful model enables cooperative wave scattering with both amplitude and phase control, and we provide unique shaping insights in terms of subchannel rearrangement and subspace alignment.
	% uniquely explain the extra design freedom from off-diagonal entries as subchannel rearrangement and subspace alignment.
	% while the shaping advantage from off-diagonal entries is uniquely attributed to subchannel rearrangement and subspace alignment.
	% An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
	To quantify the shaping capability of diagonal and \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
	% We uniquely attribute the shaping advantage from off-diagonal entries to subchannel rearrangement and subspace alignment.
	% Subchannel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward subchannels.
	% Subspace alignment generalizes phase matching in \gls{siso} and introduces a trade-off between multiplicative backward-forward and additive direct-indirect channel combinations.
	% Those channel shaping designs have two major implications.
	% First, they demystify the performance gain from off-diagonal entries in terms of {subchannel rearrangement} and {subspace alignment}.
	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
	% Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
	As a side product, we tackle \gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-based approach.
	Simulation results highlight that \gls{bd}-\gls{ris} provides a wider dynamic range and better trade-off on channel singular values, while its power and rate gains over diagonal \gls{ris} increase with \gls{mimo} dimensions.

@@

\begin{section}{Introduction}
	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
	This is empowered by the recent advances in \gls{ris}, a programmable metasurface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
	The most popular \gls{ris} research direction is \emph{joint beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
	While passive beamforming suffers severe attenuation from double fading, it usually offers a squared asymptotic behavior than active beamforming (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within channel coherence time.
	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for passive uplink communication \cite{Liang2020,Zhao2022a,Yang2024}.
	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
	This provides a ubiquitous wave scattering benchmark for different wireless applications and greatly simplifies the \gls{ris}-transceiver design.
	Relevant shaping metrics can be classified into two categories:
	\begin{itemize}
		\item \emph{Singular value centric:} Closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations. The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
		\item \emph{Power centric:} The second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize. The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
	\end{itemize}

	While those works offer initial glimpses into the channel shaping potential, one critical question remains unaddressed: \emph{To what extent can a passive \gls{ris} reshape the \gls{mimo} channel in terms of singular values?}
	% \begin{enumerate}
	% 	\item What is the entire achievable singular value region of a \gls{mimo} channel with \gls{ris}?
	% \end{enumerate}
	% they neither discuss the limitation
	% depict the entire singular value region nor provide a universal optimization framework.
	% It motivates the ultimate question: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels in terms of singular values?}
	% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
	The answer depends heavily on the scattering model and hardware architecture.
	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} assumed that each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
	This ideally translates to a scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the signal.
	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} that physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
	It can thus redistribute both amplitude and phase of the scattered wave with zero power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
	Such a powerful model can be realized at reduced cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
	Its beamforming superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a specific \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and unitary (a.k.a. fully-connected) \gls{ris}.
	Similar constraints were also adopted in \cite{Mishra2024}, which introduces transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} for improved spectral efficiency.
	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} block-unitary scattering matrices, but the proposed single-stream transceiver is rate-suboptimal and the problem is equivalent to \gls{siso}.
	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
	Although the results are promising, there lacks a study of \gls{bd}-\gls{ris} in general \gls{mimo} systems and its shaping potential over diagonal \gls{ris} has not been fully understood.
	% remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with \gls{mimo} dimensions.
	% While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general scenario with direct link and arbitrary group size.
	% On the other hand, \gls{bd}-\gls{ris} has been mainly investigated for beamforming and its channel shaping potential in \gls{mimo} has not been fully understood.
	% the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
	The contributions are summarized below.

	% 1. need a general study on BD-RIS x MIMO and explain the potential from off-diagonal entries
	% 2. need a general optimization framework for BD-RIS
	% 3. need a comprehensive answer to the channel shaping question
	% 4. need a low-complexity solution from shaping

@@

\begin{section}{Power Gain and Achievable Rate Maximization}\label{sc:power_rate}
	\begin{subsection}{Channel Power Gain}\label{sc:power}
		The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
		Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
		\begin{mini!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
			\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_block_unitary}}{}
		\end{mini!}
		which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary but still has no trivial solution.
		One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
		\begin{mini!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
			\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
		\end{mini!}
		which have global optimal solutions
		\begin{equation}
			\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
			\label{eq:orthogonal_procrustes_solution}
		\end{equation}
		where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid unitary \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
